Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-04-19 paper/ijcai16.tex
paper: add note to self.
paper: finalize first change.

\paolo{The automated assessment of preferences has received considerable attention,
starting with pioneering works in the OR community, such as \cite{White1984} and especially the UTA methodology \cite{jaquetlsiskos1982} giving rise to a wide variety of extensions \cite{jaquetlsiskos2001,greco2008ordinal}.}

%In the past decade a number of researchers have considered elicitation of preferences from an artificial intelligence perspective%; within the machine learning field the term preference learning has been catching up.
%While preferences are often assessed using some ad-hoc rules \cite{},
Within AI, a number researchers have proposed interactive methods that elicit
preferences in an adaptive way
\cite{chajewska2000,boutilier2002,Wang2003,boutilier2006,guo2010real,viappiani2010optimal},
observing that, by asking informative questions, it is often possible to make near-optimal decisions with only partial preference information.

@@

We implemented the {\sc SetMargin} algorithm using Python, leveraging Gurobi
6.5.0 for solving the core MILP problem. Both the {\sc SetMargin} source code
and the full experimental setup are available at 
\url{https://db.tt/oqY62odW}.

>>>>

The automated assessment of preferences has received considerable attention,
starting with pioneering works in the OR community, such as \cite{White1984}
and especially the UTA methodology \cite{jaquetlsiskos1982} giving rise to a
wide variety of extensions \cite{jaquetlsiskos2001,greco2008ordinal}.
%In the past decade a number of researchers have considered elicitation of preferences from an artificial intelligence perspective%; within the machine learning field the term preference learning has been catching up.
%While preferences are often assessed using some ad-hoc rules \cite{},
Within AI, a number researchers have proposed interactive methods that elicit
preferences in an adaptive way
\cite{chajewska2000,boutilier2002,Wang2003,boutilier2006,guo2010real,viappiani2010optimal},
observing that, by asking informative questions, it is often possible to make
near-optimal decisions with only partial preference information.

@@

We implemented the {\sc SetMargin} algorithm using Python, leveraging Gurobi
6.5.0 for solving the core MILP problem. Both the {\sc SetMargin} source code
and the full experimental setup are available at 
\url{https://db.tt/oqY62odW} \stefano{update the link!}.
